### 2021-04-10 Appendix-A/Appendix-A.tex
Updates from Overleaf

\section{Introduction}

@@

\section{Requirements}
We have tested \tool{} on both macOS and Ubuntu. You can refer to the continuous integration scripts to build \tool{} on your operating system. However, we strongly recommend you to build \tool{} inside a container to avoid any dependency problems. To simplify the illustration, we only include the instructions of installations within the docker in this paper.
\begin{itemize}
\item Supported OS: Ubuntu 18.04
\item Memory: 32 GB (If you want to run experiments concurrently, update the size of RAM
     accordingly. Otherwise the program may be terminated by the system.)
\end{itemize}

\section{Installation}

@@

\begin{lstlisting}[language=bash]
$ ./build.sh
\end{lstlisting}
\section{Run the hello world example}
In this section, we walk you through the steps to test a simple function with \tool{}.

@@

\subsection{Mark secret data as symbolic}
In order to test this function with \tool{}, we need to mark the variable that representing the secret data as a symbolic variable. We use the function \textsf{abacus\_make\_symbolic}. The function takes three arguments: the type of the symbol, the address of the secret, and the length of the secret input. In the below example, the secret input is the variable \textsf{secret}, and its length is two bytes. We add the \textsf{main} function in Figure~\ref{fig:example1} and compile the source code into an executable.

@@

\subsection{Build the example}

@@

\subsection{Collect the trace}
We use the pin tool to collect the execution trace. The tool can automatically collect the trace and other necessary runtime information.
\begin{lstlisting}[language=bash]
$ cd /abacus/Pintools
$ make PIN_ROOT=/abacus/Intel-Pin-Archive/ TARGET=ia32
$ cd /abacus
$ /abacus/Intel-Pin-Archive/pin \ 
  -t Pintools/obj-ia32/MyPinToolLinux.so \
  -- ./examples/a.out 
\end{lstlisting}

@@

\subsection{Quantify the leakage}
To analyze the execution trace and generate the report, run the below command:
\begin{lstlisting}[language=bash]
$ ./build/App/QIF/QIF ./Inst_data.txt -f Function.txt \ 
  -d ./examples/a.out -o result.txt
\end{lstlisting}

@@

\section{Analyze Cryptography Function}
We have applied \tool{} on the following libraries:
\begin{itemize}
\item OpenSSL: 0.9.7, 1.0.2f, 1.0.2k, 1.1.0f, 1.1.1, 1.1.1g
\item MbedTLS: 2.5, 2.15
\item Libgcrypt: 1.8.5
\item Monocyper: 3.0
\end{itemize}

@@

\section{Command-line Options}
\tool{} takes the trace file as the input (\textsf{Inst\_data.txt}). Besides the trace file, \tool{} has the following command-line options:
\vspace{6pt}
\\\textsf{-d {<executable file>}}
\\ Read an elf \textit{executable file}. \tool{} can parse the debug information inside the file. With the optional input, \tool{} is able to output which line in the original source code actually leaks the sensitive information.
\vspace{6pt}
\\\textsf{-f {<function file>}}
\\Read a function file that was generated by the Pin tool. The command is optional. With the optional input, \tool{} is able to output which function leaks the information and call sites from the sensitive buffer to the leaked site.
\vspace{6pt}
\\\textsf{-n {<Monte Carlo times>}}
\\ Set the times of Monte Carlo Sampling when \tool{} estimates the amount of leakage information. If you do not specify the option, \tool{} can automatically terminate the sampling when the tool has 95\% confidence that the error of estimated leaked information is less than 1 bit. Please refer to the paper if you want to learn more about the details.
\vspace{6pt}
\\\textsf{-a {<the address of the secret buffer>} \\-s {<the size of the buffer>}}
\\The two input options must be used together. In the previous example, we use \textsf{abacus\_make\_symbolic} to mark the secret buffer. For a raw binary, we use the above two options to tell \tool{} which buffer is the secret and its length.

>>>>

\section*{Introduction}

@@

\section*{Requirements}
We have tested \tool{} on both macOS and Ubuntu. You can refer to the continuous integration scripts to build \tool{} on your operating system. However, we strongly recommend you to build \tool{} inside a container to avoid any dependency problems. To simplify the illustration, we only include the instructions of installations within the docker in this paper.
\begin{itemize}
\item Supported OS: Ubuntu 18.04
\item Memory: 32 GB (If you want to run experiments concurrently, update the size of RAM
     accordingly. Otherwise the program may be terminated by the system.)
\end{itemize}

\section*{Installation}

@@

\begin{lstlisting}[language=bash]
$ ./build.sh
\end{lstlisting}
\section*{Run the hello world example}
In this section, we walk you through the steps to test a simple function with \tool{}.

@@

\subsection*{Mark secret data as symbolic}
In order to test this function with \tool{}, we need to mark the variable that representing the secret data as a symbolic variable. We use the function \textsf{abacus\_make\_symbolic}. The function takes three arguments: the type of the symbol, the address of the secret, and the length of the secret input. In the below example, the secret input is the variable \textsf{secret}, and its length is two bytes. We add the \textsf{main} function in Figure~\ref{fig:example1} and compile the source code into an executable.

@@

\subsection*{Build the example}

@@

\subsection*{Collect the trace}
We use the pin tool to collect the execution trace. The tool can automatically collect the trace and other necessary runtime information.
\begin{lstlisting}[language=bash]
$ cd /abacus/Pintools
$ make PIN_ROOT=/abacus/Intel-Pin-Archive/ TARGET=ia32
$ cd /abacus
$ /abacus/Intel-Pin-Archive/pin \ 
  -t Pintools/obj-ia32/MyPinToolLinux.so \
  -- ./examples/a.out 
\end{lstlisting}

@@

\subsection*{Quantify the leakage}
To analyze the execution trace and generate the report, run the below command:
\begin{lstlisting}[language=bash]
$ ./build/App/QIF/QIF ./Inst_data.txt -f Function.txt \ 
  -d ./examples/a.out -o result.txt
\end{lstlisting}

@@

\section*{Analyze Cryptography Function}
We have applied \tool{} on the following libraries:
\begin{itemize}
\item OpenSSL: 0.9.7, 1.0.2f, 1.0.2k, 1.1.0f, 1.1.1, 1.1.1g
\item MbedTLS: 2.5, 2.15
\item Libgcrypt: 1.8.5
\item Monocyper: 3.0
\end{itemize}

@@

\section*{Command-line Options}
\tool{} takes the trace file as the input (\textsf{Inst\_data.txt}). Besides the trace file, \tool{} has the following command-line options:
\vspace{6pt}
\\\textsf{-d {<executable file>}}
\\ Read an elf \textit{executable file}. \tool{} can parse the debug information inside the file. With the optional input, \tool{} is able to output which line in the original source code actually leaks the sensitive information.
\vspace{6pt}
\\\textsf{-f {<function file>}}
\\Read a function file that was generated by the Pin tool. The command is optional. With the optional input, \tool{} is able to output which function leaks the information and call sites from the sensitive buffer to the leaked site.
\vspace{6pt}
\\\textsf{-n {<Monte Carlo times>}}
\\ Set the times of Monte Carlo Sampling when \tool{} estimates the amount of leakage information. If you do not specify the option, \tool{} can automatically terminate the sampling when the tool has 95\% confidence that the error of estimated leaked information is less than 1 bit. Please refer to the paper if you want to learn more about the details.
\vspace{6pt}
\\\textsf{-a {<the address of the secret buffer>} \\-s {<the size of the buffer>}}
\\The two input options must be used together. In the previous example, we use \textsf{abacus\_make\_symbolic} to mark the secret buffer. For a raw binary, we use the above two options to tell \tool{} which buffer is the secret and its length.
